Rubin Observatory Scheduling Algorithm and Simulations

### 2022-07-27 ms.tex
change software

\software{Astropy \citep{astropy2013, astropy2018}} 
\software{Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019}}
\software{Numpy \citep{harris2020array}}
\software{Matplotlib \citep{Hunter:2007}}
\software{Scipy \citep{2020SciPy-NMeth}}
\software{Pandas \citep{jeff_reback_2022_6702671}}
\software{Scikit-learn \citep{scikit-learn}}
\software{OpenOrb \citep{Granvik2009}}
\bibliography{bibfile}{}
\bibliographystyle{aasjournal}

>>>>

\software{Astropy \citep{astropy2013, astropy2018}, 
          Healpy and HEALpix\footnote{\url{http://healpix.sourceforge.net}} \citep{healpix2005, Zonca2019},
          Numpy \citep{harris2020array},
          Matplotlib \citep{Hunter:2007},
          Scipy \citep{2020SciPy-NMeth},
          Pandas \citep{jeff_reback_2022_6702671},
          Scikit-learn \citep{scikit-learn},
          OpenOrb \citep{Granvik2009}}

\bibliography{bibfile}{}
\bibliographystyle{aasjournal}
